RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-15 paper/two_pager.tex
Add back in note on weather

For future work, we need to actually improve the timing (as mentioned above) to
work in real time, improve robustness for a greater variety of conditions, and
to increase the generality to function on a less stable platform--our boat will
certainly be pitching and rolling substantially more than the platform we had
for this footage.

>>>>

For future work, we need to actually improve the timing (as mentioned above) to
work in real time, improve robustness for a greater variety of conditions
(including different weather), and
to increase the generality to function on a less stable platform---our boat will
certainly be pitching and rolling substantially more than the platform we had
for this footage.
